Gaussian variance estimation in simulated data sets

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

```{r install-pkgs-2, eval=FALSE}
devtools::install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
```

@@

```{r plot-mean-and-variance, fig.height=4, fig.width=5}
xgrid <- (0:10000)/10000
plot(xgrid,fTrue(xgrid),type = "l",ylim = c(-5,5),ylab = "y",xlab = "X",
     lwd = 2)
lines(xgrid,fTrue(xgrid) + 2*sqrt(gTrue(xgrid)),col = "darkorange",lwd = 2)
lines(xgrid,fTrue(xgrid) - 2*sqrt(gTrue(xgrid)),col = "darkorange",lwd = 2)
```

@@

In the first scenario, we simulated unevenly spaced data points, and
assessed accuracy by computing the mean of the squared errors (MSE)
evaluated at 201 equally spaced points.

```{r simulation-1-initialize, eval=FALSE}
mse.mu.uneven.mfvb  <- 0
mse.mu.uneven.smash <- 0
mse.sd.uneven.mfvb  <- 0
mse.sd.uneven.smash <- 0
```

@@

@@

  mse.mu.uneven.mfvb[j] <- mean((fhatMFVBgOrig - fTrue(xgOrig))^2)
  mse.sd.uneven.mfvb[j] <- mean((sqrtghatMFVBgOrig-exp((loggTrue(xgOrig))/2))^2)

@@

  mse.mu.uneven.s8[j]=mean((mu.est.inter-fTrue(xgOrig))^2)
  mse.sd.uneven.s8[j]=mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
}
cat("\n")
```

>>>>

```{r install-pkgs-2, eval=FALSE}
devtools::install_github("stephenslab/smashr")
```

@@

```{r plot-mean-and-variance, fig.height=5, fig.width=6}
xgrid <- (0:10000)/10000
plot(xgrid,fTrue(xgrid),type = "l",ylim = c(-5,5),ylab = "y",xlab = "X",
     lwd = 2)
lines(xgrid,fTrue(xgrid) + 2*sqrt(gTrue(xgrid)),col = "darkorange",lwd = 2)
lines(xgrid,fTrue(xgrid) - 2*sqrt(gTrue(xgrid)),col = "darkorange",lwd = 2)
```

@@

In the first scenario, we simulate data sets with unevenly spaced data
points, and assesse accuracy by computing the mean of the squared
errors (MSE) evaluated at 201 equally spaced points.

```{r simulation-1-initialize}
mse.mu.uneven.mfvb  <- 0
mse.mu.uneven.smash <- 0
mse.sd.uneven.mfvb  <- 0
mse.sd.uneven.smash <- 0
```

@@

  # RUN MEAN FIELD VARIATIONAL BAYES
  X     <- cbind(rep(1,n),x)
  Cumat <- cbind(X,Zu)
  Cvmat <- cbind(X,Zv)
  ncX   <- ncol(X)
  ncZu  <- ncol(Zu)
  ncZv  <- ncol(Zv)
  ncCu  <- ncol(Cumat)
  ncCv  <- ncol(Cvmat)

@@

  mse.mu.uneven.mfvb[j]<-mean((fhatMFVBgOrig - fTrue(xgOrig))^2)
  mse.sd.uneven.mfvb[j]<-mean((sqrtghatMFVBgOrig-exp((loggTrue(xgOrig))/2))^2)

@@

  mse.mu.uneven.s8[j]<-mean((mu.est.inter-fTrue(xgOrig))^2)
  mse.sd.uneven.s8[j]<-mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
}
cat("\n")
```
